\documentclass{article}[10pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{siunitx}
\graphicspath{ {Images/} }
\pgfplotsset{width=8cm,compat=1.14}


\begin{document}
\section{Wave-particle duality}
\begin{tikzpicture}
  \draw (0.2,0) node {$\boxed{{}^9_4Be}$};
  \draw [left, text width=6cm](-1,1) node {Mass: Protons plus Neutrons};
  \draw [left, text width=6cm](-1,-1) node {Atomic number: number of Electrons or Protons};
  \draw [->] (-0.15,-0.2) -- (-1.2,-0.8);
  \draw [->] (-0.15,0.1) -- (-2.3,1);
\end{tikzpicture}

\subsection{Characteristics of a Wave}
\begin{itemize}
    \item Wave Length ($\lambda$) --- Distance between two consecutive points of
          equal vibrational phase.
          \begin{center}
              \begin{tikzpicture}
              \begin{axis}
              [
                domain=0:2*pi,
                samples=200,
                no marks, grid,
                xticklabels={0, $\frac{\pi}{4}$,  $\frac{\pi}{2}$,
                             $\frac{3\pi}{4}$, $\pi$,$\frac{5\pi}{4}$,
                             $\frac{3\pi}{2}$, $\frac{7\pi}{2}$, 2$\pi$},
                xtick={0, 0.7853,...,6.2832},
                ymax=1.5
              ]
              \addplot {sin(deg(x))};
              \draw[<->]      (0,1.2) -- node[above] {$\lambda$} (6.2832,1.2);
              \end{axis}
              \end{tikzpicture}
          \end{center}
          \begin{align*}
              1\si{\micro\metre} = \num{e-6}\si{\metre} \\[0.5em]
              1\si{\nano\metre} = \num{e-9}\si{\metre}  \\[0.5em]
              1\si{\angstrom} = \num{e-10}\si{\metre}   \\[0.5em]
              1\si{\pico\metre} = \num{e-12}\si{\metre} \\[0.5em]
          \end{align*}
    \item Frequency ($\nu$) --- Number of vibrations or complete cycles per
          unit of time.
          \begin{align*}
              1\si{\mega\hertz} = \num{e6}\si{\hertz} \\[0.5em]
              1\si{\giga\hertz} = \num{e9}\si{\hertz} \\[0.5em]
              1\si{\tera\hertz} = \num{e13}\si{\hertz} \\[0.5em]
          \end{align*}

    \item Period ($T$) --- Duration of a cycle $V=\frac{1}{T}$

    \item Wave Number --- Number of complete cycles per unit of time
          \begin{align*}
              \bar{\nu} = \frac{1}{\lambda}
          \end{align*}
          TODO:\@ Is the name of this right?
    \item Propagation Speed --- Speed with which the wave propagates in a given
          direction.
          \begin{align*}
                \nu = \frac{c}{\lambda} \\
                \lambda = cT
          \end{align*}
          TODO:\@ Add graphics for the wave, showing with amplitude as the Y axis,
          time as the X axis, and pointing to the nodes, peaks, and minimuns or
          whatever their name is in english.
\end{itemize}
Note that the frequency, and the period are, unlike the wavelegth, independent
of the mean through which the wave travels.
\subsection{Energy of an Electromagnetic Wave}
\begin{align*}
        E &= h\nu && E=nh\nu \\
\end{align*}
Where $E$ is the energy of a photon or electron, $h$ is Planck's constant
($h = 6.62607\times 10^{-34}\si{\joule\second}$)
\subsection{Electromagnetic Spectrum}
TODO:\@ Add graphics here. It shows the different radiations from
microwave to gamma rays, there's also an image showing the combinations of RGB
lights, and it also mentions the largest and smallest (red, violet respectively)
frequencies that the human eye can see.
\subsection{Interference}
Interference is a phenomenom associated with the wave-like behavior of
electromagnetic radiation. The interference between two waves travelling through
the same region in space yields another wave, which is the algebric sum of the
two interferring waves.

TODO:\@ Graphs for constructive and destructive interferrence.
\subsection{Stationary Waves}
REVIEW NEEDED

The interference between two waves travelling at the same speed, but in opposing
directions creates a \emph{stationary wave} --- a wave in which, throughout
time, the nodes and peaks (TODO:\@ Peaks isn't the word I want, I mean the part
which is either a peak or valley) stay at the same point in space

TODO:\@ Graph for ``wave in a box'' stationary wave.

The existence of boundary conditions, beyond causing the phenomenon to be
stationary, has another important consequence.The wave functions that describe
it [the wave] cannot be ordinary. It's wavelength depends on imposed physical
constraints (in this case a distance between points in space) and differ
from each other through an integer.
\begin{align*}
    \lambda = \frac{2L}{n} \quad n=1,2,3,\ldots \\
\end{align*}
TODO:\@ I forgot how to properly align these, so I did ``\quad'' for the time
beign.

With this we can see that the solutions are discrete, as opposed to being continuous, and the
 factor distinguishing them is the integer $n$, which we call a quatum number.

TODO:\@ Add graph showing waves with different $n$'s
\subsection{Electromagnetic Radiation}
The propagation of electromagnetic radiation is a wave-like movement, and with
it we associate a period $T$, a frequency $\nu$, and a wavelength $\lambda$.
While in some cases the eletromagnetic radiation will present typical wave-like
behavior, such as diffraction, on others it behaves in  a particle-like manner.
One example of the particle-like nature of radiation is the well known
``photoelectric effect'' experiment.

TODO:\@ Diagram of the photoelectric setup.

From this experiment we could verify that:
\begin{enumerate}
    \item The emission of electrons on off the plate depends on the frequency of
          the incident radiation, and not on the intensity of the inciding beam.
    \item The number of emitted electrons is proportional to the intensity of
          the beam
    \item Emission is imediate, even for low-intensity beams.
    \item Electrons bind (connect) to the metal with an energy $W$, which has to
          the incident beam must provide to release the electron. The kinetic
          energy of said electron is such that:
          \begin{align*}
              E_c &= \frac{1}{2}\si{\metre\newton}^2 = E_{\text{photon}} - W \\
              E_c &= h\nu - W \\
          \end{align*}
          TODO:\@ Properly align these.\\
\end{enumerate}
Below a certain \emph{critical frequency} $\nu_0$, there will be no
photoemission, because the energy $h\nu$ is insufficient to ``beat''
the attraction potential $W$. We then have
$$h\nu_0 = W$$
TODO:\@ Add the graph that is at the beginning of page 5.

The intensity of the inciding beam will be a measurement of the number of
\emph{quanta} transmitted by the radiation, given that the higher the intensity
the more photons are emitted per unit of time. The interpretation of the
photoelectric effect suggests that light is a particle, and that the energy for
each transmitted particle is $h\nu$. Einstein named these particles \emph{photons}.

In other experiments, such as the dark-body emission, the particle-like
description of light is the only one compatible with the results. We can now see
that the wave-like and particle-like aspects of light are intimately associated,
and that the best description of radiation is a \emph{dual} one.
\subsection{de-Broglie Hypothesis}
TODO:\@ Insert all the formulas at the end of page 5. Take care of formatting
them in a sensible way.

de-Broglie, with the dualistic properties of radiation in mind,
proposed that this type of behavior, verified for electromagnetic radiation,
would be valid for all the other entities which had, up until that point, been
identified as particles. He would later describe this idea with the
relation:
$$\lambda = \frac{h}{p}$$
\subsection{Electrons}
\begin{itemize}
    \item Particle-like Behavior
          \begin{itemize}
              \item The determination of the mass of the electron attributed to
                    it a particle-like characteristic.
          \end{itemize}
    \item Wave-like Behavior
          \begin{itemize}
              \item Electrons suffer difraction when interferring with crystals.
          \end{itemize}
\end{itemize}
\subsection{Heisenberg's Uncertainty Principle}
A direct consequence of the dualistic behavior is the impossibily of measuring
with precision the position and the momentum of a particle. Subsequently we
must, at the quantum level, abandon the concept of trajectory since, to describe
it we must know at any given time the position and momentum of a given particle.
\subsection{Schrödinger's Equation}
\begin{align*}
    E = E_p + E_k \implies E\psi = (E_p + E_k)\psi \\
    \implies -\frac{h^2}{8\pi^2 m}\frac{d^2\psi(x)}{dx^2} + E_p\psi(x) = E_{\psi(x)}
\end{align*}

TODO:\@ Add the following as a ``subtitle'' to the equations, `Time independent
Schrödinger equation on 1 dimension, describing any system that exibits
particle-wave behavior'

Where $\psi$ is the wave function.
\subsection{Physical Interpretation of Schrödinger's solutions}

The wave function $\psi(x)$ does not have any physical meaning at first, but
it's square $\psi{(x)}^2$ is proportional to the density of particles at the point
$x$. If $\psi(x)$ represents a single particle, it's square will be
\end{document}
